### 2013-02-16 doc/icml2013/intro.tex
Updated figures

% Twist
In mixture of linear regressions, using third-order moments does not
directly reveal the tensor structure of the problem, so we cannot
directly apply the above tensor factorization techniques.  Our solution
is to employ low-rank linear regression
\cite{NegahbanWainwright2009,Tomioka2011} on second and third powers of
the response to recover the appropriate symmetric tensors, from which we
can then apply the tensor power method to retrieve the final parameters.

>>>>

% Twist
In mixture of linear regressions, using third-order moments does not
directly reveal the tensor structure of the problem, so we cannot
directly apply the above tensor factorization techniques.  Our solution
is to employ low-rank linear regression
\cite{NegahbanWainwright2009,Tomioka2011} on second and third powers of
the response to recover the appropriate symmetric tensors, using which we
can then apply the tensor power method to retrieve the final parameters.

### 2013-02-16 doc/icml2013/regression.tex
Updated figures

\paragraph{Low-rank Regression}
%\label{sec:regression}

We now bound the error of
the compound parameter estimates,
$\|\Delta_2\|_F^2$ and $\|\Delta_3\|_F^2$,
where $\Delta_2 \eqdef \hat M_2 - M_2$
and $\Delta_3 \eqdef \hat M_3 - M_3$.

>>>>

\paragraph{Low-rank Regression}
%\label{sec:regression}
\vspace{-0.5em}
We now bound the error of
the compound parameter estimates,
$\|\Delta_2\|_F^2$ and $\|\Delta_3\|_F^2$,
where $\Delta_2 \eqdef \hat M_2 - M_2$
and $\Delta_3 \eqdef \hat M_3 - M_3$.
